---
title: "Statistical Inference Course Project"
author: "echf"
date: "23/8/2021"
output: html_document
---

# Synopsis


##### This report is part of Statistical Inference course from Johns Hopkins University (Coursera).

### It consists of two parts:

##### 1. A simulation exercise.

######       will compare the exponential distribution in R with the Central Limit Theorem.

##### 2. Basic inferential data analysis.

######       I will analyze (very basically) the ToothGrowth data in the R datasets package.


### Part 1 : Simulation exercise with exponentials

##### Generate 175 random values from a normal distribution of mean 3 and standard deviation 2 (uses seed 113) 

```{r,echo = TRUE}
options(width=80)
set.seed(113) 
datos<-rnorm(175,3,2)
head(datos)
```
##### Now let's see two important data such as the mean and variance of the data 

```{r,echo = TRUE}
mean(datos)
var(datos)
```
##### Now let's see the histogram reflecting the distribution of the information 
```{r,echo = TRUE}
 hist(datos)
```

##### Relative frequencies are represented and it is possible to make a comparison with the theoretical density function. This comparison is done by executing the following code below. 
```{r,echo = TRUE}
 hist(datos, freq=FALSE)
 curve(dnorm(x,3,2),add=TRUE)
```

##### From the above we can see how the sample data are distributed against the density they show, so we see the central limit theorem. 

### Part 2 : basic inferential data analysis with ToothGrowth dataset

```{r,echo = TRUE}

```



```{r,echo = TRUE}
```







